\section{Preface}
In this project the goal is to use an image sensor to characterize and map a maze in real life units. This means that, presented with a picture of a maze, and the information about where the picture was taken from, our final implementation should be able to recognize and map the walls of the maze. This is no easy task, and will require the implementation of several different techniques working in unison.\\

To lay the groundwork for how I go about solving this task, I will first present relevant theory on the subject of digital image processing, edge detection and mapping. Some of the groundwork in the edge detection part of the report has previously been explained and researched by Tøraasen in 2009 \cite{tor}. I will still go through the most used edge detection algorithms and determine which one will be the most beneficial for my application.\\

Next the implementation of the theory will be presented. This software is the solution to our problem description and will be examined thoroughly. The implementation is written in Matlab, but is explained in detail. The implementation part of the project report will demonstrate how I go about mapping the maze given an image.\\

Testing and verification of the implemented theory is also explained. This part of the project report will determine how successful our implementation is, and also present us to potential sources of errors which will be examined in the next section. Since we are using many image processing techniques and algorithms, the potential for errors is quite large.\\

Then I will discuss our findings and compare them to the mapping accuracy and reliability of the Lego robots previously used for the task. Here I will try and explain if and how our application improves the mapping of the maze compared to the existing solutions. \\

Lastly I will see if any conclusions can be drawn given the results and discussion of the work done in this project. This implementation is different from what has previously been done earlier, so I cannot conclude as strongly as if there were other existing reports on my implementation.







