\begin{thebibliography}{99}
\bibitem{g}
    Gonzalez, R. C., \& Woods, R. E. (2010). \emph{Digital Image Processing} 3rd Edition. Pearson Education, Inc.
    
\bibitem{s}
	Leachtenauer, Jon C.  \& Driggers, Ronald. (2000). \emph{Surveillance and Reconnaissance Imaging Systems: Modeling and Performance Prediction}
    
\bibitem{mh}
	Marr, D., \& Hildreth, E. (1980). \emph{Theory of Edge Detection. Proceedings of the Royal Society of London. Series B, Biological Sciences, 207}(1167), 187-217. Retrieved from \url{http://www.jstor.org/stable/35407}

\bibitem{cam}
	Image Sensor Business Division, DSBG. \emph{Sony IMX377CQT Product Summary, Ver. 1.5} Retrieved from \url{http://www.sony-semicon.co.jp/products_en/IS/sensor2/products/imx377.html}
    
\bibitem{hough}
	Hough, P. V. C. (1962). \emph{Methods and Means for Recognizing Complex Patterns} U.S. Patent 3,069,654.
    
\bibitem{lens}
	J. Heikkila \& O. Silven, \emph{A four-step camera calibration procedure with implicit image correction}. Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition, San Juan, 1997, pp. 1106-1112.
doi: 10.1109/CVPR.1997.609468

\bibitem{ese}
	Ese, E., \emph{Sanntidsprogrammering på samarbeidande mobil-robotar}. Master 2016
    
\bibitem{ese2}
	Ese, E., \emph{Fjernstyring av legorobot}. Prosjekt 2015
    
\bibitem{mw}
	MathWorks. Library of built in functions in Matlab, and their description. \url{https://se.mathworks.com}
    
\bibitem{tor}
	Tøraasen, J. K \emph{Kartlegging ved hjelp av robot og kamerasensor}. Prosjekt 2009
    
\bibitem{image}
	Fisher, R. \emph{Image Processing Learning Resources - Laplacian of Gaussian}. Retrieved from \url{http://homepages.inf.ed.ac.uk/rbf/HIPR2/log.htm}

\bibitem{gsdcalculator}
	Pix4D. \emph{GSD Calculator}. Retrieved from \url{https://support.pix4d.com/hc/en-us/articles/202560249-TOOLS-GSD-Calculator}
    
\end{thebibliography}